\section{Introduction}
\label{sec:intro}

The intersection of generative AI and software engineering has sparked a revolution in
verifiable code generation~\cite{Schick2023,Ouyang2022}.
By integrating execution feedback via Reasoning and Acting (Re-Act) or self-reflection
(Reflexion) loops~\cite{Yao2023,Shinn2023}, Large Language Models (LLMs) can iteratively
debug logical errors in general-purpose programming contexts.
However, applying these autonomous agents to spatial and physical
environments---such as Computer-Aided Design (CAD), robotics kinematics, and
architectural synthesis---exposes a critical limitation.
These environments demand not only logical syntax correctness but strict geometric
equivariance and continuous parameter precision.
A Python script that is logically sound but spatially inverted is entirely invalid in a
manufacturing pipeline.

The transition from explicit 3D representations (\eg, point clouds, voxels, and implicit
meshes)~\cite{Nichol2022,Jun2023} to programmatic CAD
generation~\cite{Willis2021fusion,Wang2024sketch} perfectly exemplifies this challenge.
Generating an executable CAD script (\eg, using CadQuery or OpenSCAD) offers immense
advantages: parametric editability, infinite resolution, and absolute topological
guarantees.
Nevertheless, scaling this approach faces a severe data bottleneck.
High-quality Supervised Fine-Tuning (SFT) data containing \emph{Ops JSON (semantic
intent), executable CadQuery code, multi-view renders, and verified STEP geometry} is
desperately needed to train instruction-following CAD models.
Yet, aligned multi-modal datasets of this fidelity remain exceptionally scarce, primarily
due to the astronomical cost of manual human verification.

Recent advancements utilize Vision-Language Models (VLMs) as autonomous agents to bridge
this gap by attempting to write and debug CAD code directly from sketches or intent
logs~\cite{Wang2024qwen2vl}.
VLMs excel at visual-semantic alignment, correctly inferring macroscopic topologies.
For example, a modern VLM can accurately look at an engineering drawing and determine the
need for a flanged cylinder with a specific array of mounting holes.
Yet, when executing deterministic mapping rules (\eg, mapping a Fusion360 XZ-plane to an
exact axis negation in a CadQuery \texttt{Workplane}), probabilistic VLMs frequently fail.
They generate geometrically invalid, 90\textdegree-rotated models, or invert arc
directions, plummeting the 3D Intersection over Union (IoU) to near zero.

Standard automated workflows attempt to fix these spatial errors using execution-based
Re-Act loops.
We argue, however, that probabilistic Re-Act is fundamentally mismatched for
deterministic parametric repair.
Even when augmented with high-fidelity visual feedback (\eg, rendering the incorrect
geometry and feeding it back to the VLM), prompting a VLM to ``fix an overlapping inner
hole'' forces a probabilistic neural network to perform mental analytical geometry.
This trial-and-error approach bloats the prompt context, dramatically increases API
inference costs, and frequently traps the agent in hallucination loops where parameters
are adjusted aimlessly.

To overcome this, we introduce CADLoop, a highly generalizable data curation
pipeline that implements a deterministic fallback mechanism.
CADLoop asserts a fundamental neuro-symbolic design philosophy: in strictly verifiable
environments, topology and continuous parameters must be decoupled.
We let the neural network (VLM) handle structural semantics and intent, while an explicit
unified geometric skill handles spatial mathematics and AST-level code
verification.
Instead of asking the VLM to guess the exact coordinate offset for an arc's midpoint, our
unified programmatic tool actively extracts the control coordinates, geometrically
validates cross-sectional areas against ground-truth bounding boxes, and analytically
overrides the AST nodes.

Through extensive analysis over thousands of CAD geometries, we uncover a crucial
heuristic for scalable, automated curation: the $\text{IoU} \approx 0.8$ boundary.
Generated models above this threshold possess correct skeletal structures but suffer from
deterministic parameter failures.
Correcting these ``near-misses'' provides the exact proximal optimization signal desired
for instruction tuning~\cite{Ouyang2022}, avoiding the noisy, global structural rewrites
associated with hallucinated ($\text{IoU} < 0.5$) geometry.
By aggressively filtering out extreme topological failures (which are often caused by
unavoidable token limits on highly complex input sketches), CADLoop deliberately acts as a
high-precision data distillation engine, prioritizing data quality over raw scale.

\noindent\textbf{Our main contributions are summarized as follows:}
\begin{itemize}
  \item \textbf{An Equivariant-Aware Fallback Mechanism:} We propose a neuro-symbolic
        tool-use layer that steps in precisely when VLM Re-Act loops hit a reasoning
        ceiling.
        By deploying a unified geometric skill, we deterministically resolve spatial code
        errors via exact mathematical verification.
  \item \textbf{The Proximal Boundary Insight:} We provide a
        rigorous empirical demonstration showing that targeting near-miss geometric
        mismatches isolates the optimal SFT learning signal without introducing structural
        noise.
  \item \textbf{A Verified Multi-Modal Dataset:} We release a highly curated dataset of
        1646 verified pairs ($\text{IoU} \ge 0.99$), comprehensively linking structured
        Ops JSON, executable CadQuery code, 2D renders, and 3D STEP files, setting a new
        benchmark for programmatic CAD training data.
\end{itemize}
