\section{Related Work}
\label{sec:related}

To contextualize the contributions of CADLoop, we review prior literature across
two converging research directions: programmatic CAD generation and
neuro-symbolic tool-augmented agents.

\subsection{Programmatic CAD Generation and Data Curation}

Early approaches to 3D generation primarily focused on unconstrained
representations such as Neural Radiance Fields (NeRFs), point clouds,
and implicit surfaces~\cite{mildenhall2020nerf,nichol2022improved}.
While these formats are well-suited for neural generative models,
industrial computer-aided design (CAD) workflows require precise
parametric representations such as Boundary Representations (B-Rep),
where geometric entities and constraints must remain analytically
consistent.

To enable learning on parametric CAD data, several datasets and
benchmarks have been proposed. The ABC Dataset~\cite{koch2019abc}
released millions of raw STEP files, providing large-scale access to
CAD geometries. However, it lacks the procedural construction history
required to understand how a design was created.
DeepCAD~\cite{wu2021deepcad} addressed this limitation by extracting
construction sequences from CAD programs, but the representation relies
on a simplified Domain Specific Language (DSL) that lacks the expressive
power of general-purpose CAD programming environments.

More recent datasets attempt to bridge geometry and design intent.
The Fusion360 Gallery~\cite{willis2021sketch} introduced sketch graphs
and operation sequences (Ops JSON), capturing higher-level human design
intent. However, it does not provide verified executable programs,
which limits its usefulness for training code-generating models.

Recent works have explored program synthesis for CAD generation.
CAD-SIGNet~\cite{khan2024cadsignet} learns sketch-to-program mappings by
predicting parametric constraints and geometric relationships.
Cadrille~\cite{kolodiazhnyi2025cadrille} investigates reinforcement
learning for CAD code generation, demonstrating that multimodal
feedback from rendered geometry can improve generation quality.
Similarly, CAD-Recode~\cite{rukhovich2024cadrecode} and
SketchGen~\cite{wang2024sketch} attempt to generate executable CAD
programs directly from sketches, point clouds, or images.

Despite these advances, existing approaches consistently struggle to
maintain strict geometric constraints such as parallelism,
concentricity, or Boolean consistency during generation.
This is particularly problematic for program-based CAD models,
where even single-parameter deviations can lead to invalid geometry.

CADLoop addresses this challenge from a complementary perspective.
Rather than directly training a generative model, we introduce a
neuro-symbolic data curation pipeline that automatically verifies and
repairs near-miss CAD programs using deterministic analytical tools.
By identifying a high-density regime of structurally correct but
parameter-misaligned programs (IoU $\approx$ 0.8), CADLoop produces a
large-scale dataset of verified program–geometry pairs. This dataset
provides clean supervision signals for future multimodal CAD
generation models.

\subsection{Neuro-Symbolic Reasoning and Tool-Use Agents}

The limitations of pure neural reasoning in arithmetic, logic, and
spatial tasks are well-documented. To mitigate this, recent work has
explored tool-augmented large language models that delegate
deterministic computation to external programs.
Toolformer~\cite{schick2023toolformer} and
ViperGPT~\cite{suris2023vipergpt} demonstrate that offloading
structured computations to external APIs or Python environments
significantly improves reasoning accuracy in question answering and
visual reasoning tasks.
In the domain of code generation, frameworks such as
LEVER~\cite{ni2023lever} and Reflexion~\cite{shinn2023reflexion}
verify LLM outputs through execution feedback, enabling iterative
self-correction.

However, applying standard ReAct-style reasoning~\cite{yao2023react}
to spatial environments introduces a unique failure mode.
In CAD generation, visual-spatial feedback (e.g.,
``the inner hole area is too large'') represents a \emph{continuous}
error landscape rather than a discrete logical bug.
When faced with continuous errors, LLMs struggle to infer the precise
numerical adjustments required.
Furthermore, providing an agent with many fragmented mathematical
tools often leads to tool misrouting and context confusion.

CADLoop advances the neuro-symbolic paradigm~\cite{ellis2021dreamcoder}
by introducing explicit \emph{parametric grounding}.
Instead of exposing the model to numerous specialized tools,
we provide a single cohesive geometric skill
(\texttt{cad\_data\_generation}) that analytically parses,
computes, and rewrites the CAD program's Abstract Syntax Tree (AST).
This design decouples structural reasoning from numerical execution,
allowing the VLM to focus on topological intent while deterministic
geometry solvers resolve continuous constraints.