{\small
\begin{thebibliography}{99}

\bibitem{schick2023toolformer}
T.~Schick, J.~Dwivedi-Yu, R.~Dess{\`i}, R.~Raileanu, M.~Lomeli,
E.~Hambro, L.~Zettlemoyer, N.~Cancedda, and T.~Scialom.
Toolformer: Language models can teach themselves to use tools.
In \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2023.

\bibitem{ouyang2022rlhf}
L.~Ouyang, J.~Wu, X.~Jiang, D.~Almeida, C.~Wainwright,
P.~Mishkin, C.~Zhang, and others.
Training language models to follow instructions with human feedback.
In \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2022.

\bibitem{yao2023react}
S.~Yao, J.~Zhao, D.~Yu, N.~Du, I.~Shafran,
K.~Narasimhan, and Y.~Cao.
ReAct: Synergizing reasoning and acting in language models.
In \emph{International Conference on Learning Representations (ICLR)}, 2023.

\bibitem{shinn2023reflexion}
N.~Shinn, F.~Labash, and A.~Gopinath.
Reflexion: Language agents with verbal reinforcement learning.
In \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2023.

\bibitem{nichol2022pointe}
A.~Nichol, H.~Jun, P.~Dhariwal, P.~Mishkin, and M.~Chen.
Point-E: A system for generating 3D point clouds from complex prompts.
\emph{arXiv preprint arXiv:2212.08751}, 2022.

\bibitem{jun2023shapee}
H.~Jun and A.~Nichol.
Shape-E: Generating conditional 3D implicit functions.
\emph{arXiv preprint arXiv:2305.02463}, 2023.

\bibitem{willis2021fusion360}
K.~D.~D. Willis, Y.~Pu, J.~Luo, H.~Chu,
T.~Du, J.~G. Lambourne, A.~Solar-Lezama, and W.~Matusik.
Fusion 360 Gallery: A dataset and environment for programmatic CAD
construction from human design sequences.
\emph{ACM Transactions on Graphics (SIGGRAPH)}, 40(4), 2021.

\bibitem{wang2024sketchgen}
Y.~Wang, Z.~Liu, and others.
SketchGen: Generating parametric CAD programs from sketches.
\emph{arXiv preprint arXiv:2405.XXXX}, 2024.

\bibitem{wang2024qwen2vl}
P.~Wang, W.~Li, S.~Gao, and others.
Qwen2-VL: Enhancing vision-language models' comprehension of the world
at any resolution.
\emph{arXiv preprint arXiv:2409.12191}, 2024.

\bibitem{mildenhall2020nerf}
B.~Mildenhall, P.~Srinivasan, M.~Tancik,
J.~T. Barron, R.~Ramamoorthi, and R.~Ng.
NeRF: Representing scenes as neural radiance fields for view synthesis.
In \emph{European Conference on Computer Vision (ECCV)}, 2020.

\bibitem{koch2019abc}
S.~Koch, A.~Matveev, Z.~Jiang,
F.~Williams, A.~Artemov, E.~Burnaev,
M.~Alexa, D.~Zorin, and D.~Panozzo.
ABC: A big CAD model dataset for geometric deep learning.
In \emph{Proceedings of the IEEE/CVF Conference on Computer Vision
and Pattern Recognition (CVPR)}, 2019.

\bibitem{wu2021deepcad}
R.~Wu, C.~Xiao, and C.~Zheng.
DeepCAD: A deep generative network for computer-aided design models.
In \emph{Proceedings of the IEEE/CVF International Conference on
Computer Vision (ICCV)}, 2021.

\bibitem{willis2021sketch}
K.~Willis, P.~K. Jayaraman,
J.~G. Lambourne, H.~Chu, and Y.~Pu.
Engineering sketch generation for computer-aided design.
In \emph{Proceedings of the IEEE/CVF Conference on Computer Vision
and Pattern Recognition (CVPR)}, 2021.

\bibitem{khan2024cadsignet}
M.~S. Khan, E.~Dupont, and others.
CAD-SIGNet: CAD language inference from point clouds using
layer-wise sketch instance guided attention.
In \emph{Proceedings of the IEEE/CVF Conference on Computer Vision
and Pattern Recognition (CVPR)}, 2024.

\bibitem{suris2023vipergpt}
D.~Sur\'is, S.~V.~A. Suri, and A.~A. Efros.
ViperGPT: Visual inference via python execution for reasoning.
In \emph{Proceedings of the IEEE/CVF International Conference on
Computer Vision (ICCV)}, 2023.

\bibitem{ni2023lever}
A.~Ni, Z.~Yang, S.~H. Lin, and others.
LEVER: Learning to verify language-to-code generation with execution.
In \emph{International Conference on Machine Learning (ICML)}, 2023.

\bibitem{ellis2021dreamcoder}
K.~Ellis, C.~Wong, M.~Nye, M.~Sabl{\'e}-Meyer,
L.~Morales, L.~Hewitt, A.~Solar-Lezama,
and J.~Tenenbaum.
DreamCoder: Bootstrapping inductive program synthesis with wake-sleep learning.
In \emph{ACM SIGPLAN Conference on Programming Language Design and Implementation (PLDI)}, 2021.

\bibitem{rukhovich2024cadrecode}
D.~Rukhovich, V.~Kurenkov, and A.~Konushin.
CAD-Recode: Reverse engineering CAD models from point clouds via program synthesis.
\emph{arXiv preprint arXiv:2412.14042}, 2024.

\bibitem{kolodiazhnyi2025cadrille}
M.~Kolodiazhnyi, D.~Tarasov, D.~Zhemchuzhnikov,
A.~Nikulin, I.~Zisman, A.~Vorontsova,
A.~Konushin, V.~Kurenkov, and D.~Rukhovich.
Cadrille: Multi-modal CAD reconstruction with online reinforcement learning.
\emph{arXiv preprint arXiv:2505.22914}, 2025.

\bibitem{nichol2021improved}
A.~Nichol and P.~Dhariwal.
Improved denoising diffusion probabilistic models.
In \emph{International Conference on Machine Learning (ICML)}, 2021.

\bibitem{openai2025codex}
OpenAI.
GPT-5.2-Codex: An agentic coding model.
Online technical report, 2025.

\bibitem{anthropic2026opus}
Anthropic.
Claude Opus 4.6.
Online technical report, 2026.


\end{thebibliography}
}
