\appendix

\section{Datasheet for BenchCAD}
\label{app:datasheet}

We follow the datasheet template of Gebru et al.\ (2021); responses below are condensed for the appendix and reproduced in full as a separate Croissant 1.0 metadata file shipped with the dataset release.

\paragraph{Motivation.}
\textbf{For what purpose was the dataset created?} BenchCAD was created to evaluate the parametric-CAD capabilities of large vision-language and code-language models along three sub-capabilities (visual perception, parametric abstraction, code synthesis) on industrially representative part families with execution-verified ground truth.
\textbf{Who created the dataset and on behalf of which entity?} The authors. (Anonymised for double-blind submission.)
\textbf{Who funded the dataset?} The authors' affiliated institutions. (Anonymised.)

\paragraph{Composition.}
\textbf{What do the instances represent?} Each instance is a parametric CAD part: an executable CadQuery Python program, the resulting STEP file, four canonical-view PNG renders, a parameter JSON, and an op-list JSON. \textbf{How many instances are there in total?} 17{,}900 verified procedural parts, 2{,}400 paired QA questions (each evaluated under both visual and code conditioning, yielding 4{,}800 records), 748 curated edit pairs, 530 stratified Lite samples, 726 Fusion360-derived samples, 920 DeepCAD-derived samples, and 162{,}000 GenCAD-derived training pairs. \textbf{Does the dataset contain all possible instances?} No --- BenchCAD-Synth samples a subset of the parameter space per family; the schema permits unbounded sampling under the documented constraints. \textbf{Is there a label/target?} The CadQuery source code, STEP, parameters, and op list jointly serve as ground truth; for QA tasks, gold answers are derived deterministically from parameters; for edit tasks, target code and target STEP are paired with the original.

\paragraph{Collection process.}
\textbf{How was the data acquired?} Procedurally generated by the CadGen pipeline (\S\ref{sec:dataset}); the only human-in-the-loop component is edit-pair curation by the authors. \textbf{Who was involved in data collection?} The authors. \textbf{Were any ethical review processes conducted?} Not applicable; no human-subjects data.

\paragraph{Preprocessing/cleaning/labeling.}
\textbf{Was preprocessing/cleaning done?} Verification (IoU $\geq 0.99$ rotation-invariant against the builder solid; non-degenerate volume; 30\,s timeout) is the sole filter applied to BenchCAD-Synth. The Fusion360 and DeepCAD subsets undergo additional curation: parsing failures and parts whose reconstruction yields invalid geometry are excluded. \textbf{Was the raw data saved?} Yes; the unverified pre-filter output is retained for analysis and is available on request.

\paragraph{Uses.}
\textbf{Has the dataset been used for any tasks already?} The five tasks defined in \S\ref{sec:tasks}. \textbf{Is there anything that prevents responsible reuse?} The dataset contains no PII, no copyrighted source designs, and no safety-sensitive specifications. The standard-anchored families reference public ISO/DIN/EN/ASME/IEC standard codes by number and name; we do not redistribute the standard documents themselves.

\paragraph{Distribution.}
\textbf{Will the dataset be distributed?} Yes, on Hugging Face under \texttt{BenchCAD/cad\_bench} and \texttt{BenchCAD/cad\_bench\_edit}. \textbf{When?} On submission acceptance (or on arXiv release if earlier). \textbf{Under what licence?} CC-BY-4.0 for data; MIT for code (CadGen pipeline, evaluation harness, baseline checkpoint). \textbf{Are there restrictions?} Standard CC-BY-4.0 attribution.

\paragraph{Maintenance.}
\textbf{Who will support the dataset?} The authors via the GitHub issue tracker and Hugging Face dataset card. \textbf{How will errata be communicated?} Versioned releases on Hugging Face with changelogs in the dataset card.

\section{Question Bank Construction}
\label{app:qbank}

The numeric-QA tasks (\texttt{qa\_img}, \texttt{qa\_code}) draw from a per-family question bank constructed in three steps. (1) For each family, a domain-knowledge author writes 6--12 question \emph{templates} parameterised by the family's exposed parameters --- e.g.\ for \texttt{involute\_gear}: \emph{``what is the ratio of root-to-tip diameter?''}, \emph{``how many teeth does the visible gear have?''}. Templates are typed (ratio, integer count, ordinal) and constrained to be scale-invariant. (2) Templates are instantiated per-record by deterministic substitution of the verified parameter values, yielding a gold answer alongside each question. (3) A second author reviews each instantiation for ambiguity and visibility (a question must be answerable from the four canonical views with no occluded features). The final bank contains 2{,}400 unique (question, gold answer) pairs sampled across 17{,}900 records --- each evaluated under both visual (\texttt{qa\_img}) and code (\texttt{qa\_code}) conditioning, yielding 4{,}800 total QA records. The composition is approximately 60\% ratio, 35\% integer count, and 5\% ordinal. We release the question-template source code so that the bank can be regenerated under alternative parameter samples.

\section{Rotation-Invariant IoU}
\label{app:iou}

We compute IoU as the maximum over the 6-element face-up cube symmetry group (or the full 24-element rotation group; configurable). Voxelisation is at $64^3$ on the cube-normalised STEP $[-1, 1]^3$; cube normalisation centres the part at the origin and scales by the largest semi-axis. For each candidate orientation $g \in G$, we apply $g$ to the predicted voxel grid and compute IoU against the reference; the reported score is $\max_{g} \mathrm{IoU}(g \cdot \hat{V}, V)$. Implementation runs in $\approx$120\,ms per pair on a single CPU thread; the full 530-sample BenchCAD-Lite scoring completes in under one minute per model output. Source: \texttt{bench/metrics/rot\_iou.py} in the released harness.

\section{Edit Protocol}
\label{app:edit_protocol}

\paragraph{Pair construction.} The 748 BenchCAD-Edit pairs are drawn balanced across 106 families and four edit categories (balanced across dimensional, additive, subtractive, and multi-step categories). For each pair, we (i) start from a verified BenchCAD-Synth record, (ii) apply a parameter or op-list edit yielding a target part, (iii) verify the target satisfies the same IoU $\geq 0.99$ verification as the original, (iv) write a natural-language instruction by template (\emph{``increase the bore diameter to 12\,mm''}) reviewed for unambiguity by a second author, and (v) cross-validate by running two strong models and inspecting any unexpected failure modes. Pairs where models systematically disagree on instruction interpretation are revised or removed.

\paragraph{Pass@1 metric.} A model's edit is scored as a pass iff both (a) target success: $\mathrm{IoU}_{\mathrm{rot}}(\text{model edit}, \text{target}) \geq 0.99$; and (b) non-target preservation: on the spatial complement of the bounding region of the targeted feature, $\mathrm{IoU}_{\mathrm{rot}}(\text{model edit}, \text{original}) \geq 0.99$. The targeted-feature region is provided as a precomputed bounding-box annotation per pair.

\paragraph{Edit Leakage rate.} Defined as the fraction of model edits that achieve target success but fail non-target preservation: $|\{i: \text{Targ}_i \wedge \neg\text{Pres}_i\}| / |\{i: \text{Targ}_i\}|$. We additionally report a code-AST diff metric (lines changed, identifiers renamed) as a secondary measure of locality.

\section{Inference Strategy and Scoring Ablations}
\label{app:ablation}

\input{tables/tab_ablation}

Table~\ref{tab:ablation} reports four scoring-protocol and inference-strategy ablations on GPT-5.3 (think) on BenchCAD-Lite. Removing scale invariance (allowing absolute mm hints in prompts) inflates \texttt{qa\_img} by 4.6\,pt --- the systematic optimism baked into prior CAD-eval protocols. Doubling view count from 4 to 8 closes only $\leq$1.5\,pt of the Vision Bottleneck. Best-of-5 sampling and 3-turn refinement with execution feedback offer larger but ultimately bounded gains; neither approach closes more than half of the remaining gap to BenchCAD's verification threshold.

\section{CadQuery Operation Coverage}
\label{app:ops}

\input{tables/tab_op_coverage}

Table~\ref{tab:op_coverage} contrasts BenchCAD's 45+ distinct CadQuery operations against prior corpora restricted predominantly to sketch+extrude. Each ``\cmark'' indicates that the operation is exercised in at least one family/sample of the corresponding dataset, not merely supported by the underlying API.

\section{Per-Family Results}
\label{app:full_results}

\paragraph{Hard-tier families and their dependency graphs.} The hard tier concentrates families with dense parameter dependencies: involute gears (module $\times$ tooth count $=$ pitch diameter; addendum and dedendum derived from module), helical springs (free length determined by turn count $\times$ pitch), roller chains (link count constrains pitch diameter), bevel gears (ISO 23509 cone-angle relations), and twist drills (DIN 338 helix angle and point angle dependencies). These families collectively account for 89\% of the multi-step edit failures (\S\ref{sec:exp_edit}).

\paragraph{Per-family table.} A full per-family breakdown of \texttt{img2cq} pass rate, mean Chamfer distance, and Edit Leakage rate for the top eight models is included with the released harness as \texttt{results/per\_family\_lite.csv}; we omit the table from the appendix for space and to avoid implying single-cell statistical significance on small per-family sample sizes (typically 5 records per family in BenchCAD-Lite).

\section{Reproduction Recipe}
\label{app:reproduce}

The complete BenchCAD evaluation runs on a single A100 GPU in under two hours per model for BenchCAD-Lite (530 samples). Reproduction uses the released \texttt{bench/fetch\_data.py} (one-line Hugging Face fetch), the \texttt{bench.eval} runner (\texttt{--model maksimko123/cadrille-rl --task img2cq --split BenchCAD-Lite --seed 42}), and the released model's documented inference entry-point. We provide adapter wrappers under \texttt{bench/models/providers/} for cadrille and CADEvolve so that the existing runner accepts these models without modification. Per-task IoU, Chamfer distance, invalidity ratio, and per-family breakdowns are exported to \texttt{results/<task>/<model>/}.

For training the open BenchCAD baseline: \texttt{train/sft\_qwen2vl.py} with the released config, training data manifest \texttt{train/manifest\_synth\_plus\_gencad.jsonl}, and the resulting checkpoint hash. Total training time is approximately 9 GPU-hours on 8$\times$A800-80GB.

\section{Ethical Considerations and Broader Impact}
\label{app:ethics}

BenchCAD contains procedurally generated parametric CAD parts and references public engineering standards by code and name. The dataset contains no personal data, no proprietary designs, and no safety-sensitive specifications. Potential risks of CAD-capable models more broadly --- e.g.\ accelerated reverse-engineering of regulated components --- are not specific to BenchCAD and are best addressed at the model-deployment layer rather than the benchmark layer. We see no negative societal impact specific to this work that is not already present in the underlying open-source CAD ecosystem.
