\section{The BenchCAD Dataset}
\label{sec:dataset}

\paragraph{Design principles.} BenchCAD rests on four principles.
\emph{(P1) Expert-generated geometry}: every family is hand-crafted by domain experts directly from industrial standards, who solve the standard-mandated geometric equations to produce parameterised CAD models that strictly respect engineering conventions and inter-parameter constraints.
\emph{(P2) Standard-table anchoring}: where a part has an industrial counterpart, parameters sample from real specification tables (ISO 22 V-belt cross-sections, DIN 338 twist-drill diameters, ISO 23509 bevel-gear pitch--module relations); 49\% of BenchCAD families (52/106) are standard-anchored, drawing from 47 unique ISO/DIN/EN/ASME/IEC codes (full code list in Appendix~\ref{app:standards}).
\emph{(P3) Family-level taxonomy}: records are grouped into 106 named families (\texttt{coil\_spring}, \texttt{helical\_gear}, \texttt{twisted\_drill}, $\ldots$), each implemented by a small Python module exposing a typed parameter schema, sampler, validator, and deterministic builder --- making coverage measurable and per-family analysis trivial.
\emph{(P4) Operation breadth}: the dataset exercises 45+ distinct CadQuery operations spanning sketch primitives, contour drawing, workplane manipulation, sketch arrays, 3D operations (extrude, twist-extrude, revolve, loft, sweep), Booleans (union, cut), hole variants, and edge finishing (Appendix~\ref{app:ops}).



\paragraph{CadGen pipeline.} The data construction pipeline, \textbf{CadGen}, processes each family$\times$difficulty bucket through three stages:
\begin{itemize}
    \item \textbf{Parameter Sampling:} deterministic sampling under standard-table constraints from the JSON schema.
    \item \textbf{Program Emission:} the family's \texttt{make\_program} returns an op sequence consumed by a builder that produces both Python CadQuery source and a CadQuery \texttt{Workplane} object aligned by construction.
    \item \textbf{Execution \& Verification:} sandboxed re-execution; quarantine on parse error, $>30$\,s timeout to filter out complex geometries, zero/inverted volume, following by expert manual check.
\end{itemize}
As of May 2026, 17{,}900 records have passed all verification checks.

\paragraph{BenchCAD-Edit.} BenchCAD-Edit is a paired-edit subset built directly on top of BenchCAD-Synth: each record is a verified $(\text{original program}, \text{NL instruction}, \text{target program}, \text{target STEP})$ quadruple. Pairs are constructed by (i) selecting a verified BenchCAD-Synth part, (ii) applying a single parametric or op-list edit to obtain a target part, (iii) re-verifying the target through the same rotation-invariant IoU $\geq 0.99$ pipeline, (iv) writing a templated NL instruction reviewed for unambiguity by a second author, and (v) cross-validating with two strong models to surface ambiguous cases. The 748 released pairs are balanced across all 106 families and stratified into five task types (T1 \emph{literal\_replace}, T2 \emph{chain\_transform}, T3 \emph{relative\_compute}, T4 \emph{feature\_edit}, T5 \emph{geometry\_rebuild}; Appendix~\ref{app:edit_protocol}, Table~\ref{tab:task_taxonomy}), and orthogonally categorised as dimensional, additive, subtractive, or multi-step. Unlike prior CAD edit datasets that grade by code-string overlap or single-image renders, every BenchCAD-Edit prediction is graded by the rotation-invariant voxel-IoU pipeline on rebuilt STEP, with a separate non-target-preservation check that detects \emph{Industrial Common Sense Gap} failures (\S\ref{sec:exp_edit}).

\paragraph{Splits, taxonomy, hosting.} The release contains \emph{BenchCAD-Synth} (17{,}900 verified procedural parts, primary evaluation set), \emph{BenchCAD-Edit} (748 curated edit pairs across dimensional, additive, subtractive, and multi-step categories), \emph{BenchCAD-Lite} (530-sample stratified subset for fast leaderboards), \emph{BenchCAD-Fusion360} and \emph{BenchCAD-DeepCAD} (verified OOD subsets), and \emph{BenchCAD-GenCAD} (162{,}000 image$\to$code training pairs)~\citep{GenCAD2025}.
Each family supports easy/medium/hard tiers defined by parameter complexity.
Every release ships a Croissant 1.0 metadata file~\citep{Croissant2024} validated by the public checker, hosted on Hugging Face under \texttt{BenchCAD/cad\_bench} with verification-pipeline source under MIT and data under CC-BY-4.0.
Full datasheet (Appendix~\ref{app:datasheet}) and per-family schemas accompany the release.


