\section{Discussion}
\label{sec:discussion}

\paragraph{Three blocked escape routes.} BenchCAD measurements close three routes that one might hope would reduce the model--human gap without fundamental change. (i) \emph{Scaling within open-source families} (\S\ref{sec:exp_main}) yields under 15\,pt across 78$\times$ parameter expansion --- far below the 66-pt deficit to humans. (ii) \emph{Chain-of-thought reasoning} (\S\ref{sec:exp_capability}) does not close the Vision Bottleneck; it amplifies it. (iii) \emph{View-count augmentation} (Appendix~\ref{app:ablation}) recovers $\leq$1.5\,pt from 4 to 8 views, ruling out simple visual-context starvation as the explanation. Together these results suggest the path forward lies in training procedures explicitly aware of the parametric-symbolic structure of CAD geometry.

\paragraph{Why edit, not generation, is the load-bearing test.} A model that can reconstruct a part from images is impressive, but a model that can \emph{modify} an existing part is industrially useful. The Edit Leakage finding (\S\ref{sec:exp_edit}) shows that the strongest reasoning model corrupts unrelated features in 64\% of nominally successful edits, and multi-step edits requiring parameter-dependency reasoning collapse below 15\% across every model. This is the single quantitative gap that most clearly separates current models from a useful CAD copilot, and it is invisible to any prior CAD eval.

\paragraph{The CAD-specialised lineage transfers poorly.} cadrille-RL and CADEvolve, which match published $\sim$92\% IoU on DeepCAD under our scoring infrastructure, lose 28--32 points on BenchCAD-Lite (\S\ref{sec:transfer}). The drops concentrate on standard-anchored hard families (helical gears, twist drills, coil springs) and on operations absent from their sketch+extrude training corpora. SOTA improvements on existing CAD benchmarks are increasingly within-distribution; BenchCAD reopens the out-of-distribution evaluation surface.

\section{Limitations}
\label{sec:limitations}

\paragraph{Procedural data is not industrial CAD.} BenchCAD parts are sampled from parametric templates, not extracted from real engineering repositories. We mitigate this by (i) anchoring 55\% of families to published ISO/DIN/EN/ASME/IEC specification tables and (ii) including verified Fusion360 Gallery and DeepCAD subsets for OOD comparison, but our parts do not capture the full diversity of proprietary industrial design (e.g.\ hand-drawn manufacturing tolerances, undocumented design intent).

\paragraph{Standard-anchored does not mean standard-compliant.} A family declared as \texttt{standard = "ISO 23509"} samples within ISO parameter ranges and enforces inter-parameter relations from the standard, but does not validate against the full set of manufacturing tolerances or material specifications mandated by that standard. We use the term \emph{standard-anchored} throughout to mark this distinction.

\paragraph{Reference baseline is intentionally weak.} Our open BenchCAD-trained baseline (Qwen2-VL-2B SFT-only) is a community lower bound, not an attempt at SOTA. We do not apply RL, do not perform multi-task pretraining, and do not exhaust the training corpus. The 22.7\% IoU it reaches is therefore not an upper bound on what BenchCAD-trained models can achieve.

\paragraph{Edit Leakage measurement.} Our non-target preservation metric uses voxel IoU on the spatial complement of the targeted feature; this captures most leakage modes but can miss small parametric shifts whose voxel footprint is subthreshold. Appendix~\ref{app:edit_protocol} discusses the protocol, including a complementary code-AST diff metric we report alongside.

\paragraph{Human upper bound from three experts.} Our human ceiling is derived from three professional CadQuery engineers over 50 samples per task; we adjudicate disagreements by majority vote. A larger expert pool would tighten the ceiling, particularly on multi-step edits where individual variability is high.

\section{Conclusion}
\label{sec:conclusion}

We presented BenchCAD, a CAD code-generation benchmark anchored in industrial standards and decomposed across the three sub-capabilities required to map an engineering image to executable parametric source. The dataset's 20{,}143 verified parts span 106 families and exercise 45+ CadQuery operations; its five tasks (\texttt{img2cq}, \texttt{qa\_img}, \texttt{qa\_code}, \texttt{edit\_img}, \texttt{edit\_code}) include the first public CAD edit benchmark with execution-verified before/after pairs and a non-target preservation metric. Across 30+ frontier vision-language and code-language models, BenchCAD reveals two systematic phenomena: a 15--20-point Vision Bottleneck between code-conditioned and image-conditioned numeric QA scores that survives chain-of-thought, parameter scaling, and view augmentation; and an Edit Leakage rate of 64\% on nominally successful edits, with multi-step parameter-dependency edits collapsing below 15\% pass for every model. Closing these gaps will require training procedures explicitly aware of the parametric-symbolic structure of CAD geometry, not continued scaling of code-finetuned VLMs. Dataset, evaluation harness, BenchCAD-trained baseline, and Croissant metadata are released under CC-BY-4.0 at \texttt{huggingface.co/BenchCAD}.
