\section{Experiments}
\label{sec:experiments}

\subsection{Setup}
\label{sec:exp_setup}
For each task, we include a \emph{blind baseline} that preserves the output format but removes the informative input: black views for \textsc{Image-to-Code}/\textsc{Image QA}, no code for \textsc{Code QA}, and unchanged original programs for \textsc{Code Edit}. These baselines measure gains beyond dataset priors and metric floors.
% \hc{provide more details}
and quantify each model's gain over it across all relevant metrics.

\subsection{Models}
\label{sec:exp_models}

Three model classes are evaluated:
\emph{(i) Frontier proprietary MLLMs:} GPT-4o~\citep{OpenAI2024GPT4o}, GPT-5.3 thinking / non-thinking~\citep{OpenAI2026GPT53}, Claude Opus 4.7 thinking / non-thinking~\citep{Anthropic2026Claude47}, Gemini 3.1 Pro thinking / non-thinking~\citep{Google2026Gemini31}, OpenAI o3~\citep{OpenAI2025o3}, Moonshot Kimi~\citep{MoonshotAI2025Kimi}.
\emph{(ii) Open-source MLLMs / code LLMs:} Qwen3-VL~\citep{Bai2026Qwen3VL}, InternVL3~\citep{Chen2025InternVL3}, gpt-oss-120b~\citep{OpenAI2025GPTOSS}, nemotron-3-super-120b-a12b~\citep{NVIDIA2026Nemotron}.
\emph{(iii) CAD-specialist lineage:} cadrille-RL~\citep{Kolodiazhnyi2026} and CADEvolve v3~\citep{Elistratov2026}. Closed models are queried through their official APIs; open-weights models via OpenRouter~\citep{OpenRouter2024} or the official repository.


\subsection{Evaluation}
\label{sec:exp_eval}
For Vision QA and Code QA (BenchCAD-QA, 2{,}400 paired image/code numeric items), accuracy is computed under $\pm 5\%$ tolerance for ratios and exact match for integers, broken out along the four-level capability hierarchy (\S\ref{sec:capability}). For \textsc{Vision2Code} we report \texttt{exec\_pct}, mean voxel \texttt{IoU}, mean Chamfer distance \texttt{CD}, mean Hausdorff distance \texttt{HD}, Feature-F1, essential-op recall \texttt{ess}, and a composite \texttt{total} score (Table~\ref{tab:codegen_unified}). For \textsc{Edit Code}, with rendered solid $S_g$, original solid $S_o$, and target solid $S_t$, let $\mathrm{IoU}(S_a, S_b)$ denote the voxel intersection-over-union. Over $n$ records we report the normalized accuracy eliminate the bias from varying original-target IoU across edit pairs:
\begin{align}
\label{eq:edit_acc}
\mathrm{Acc}_{\mathrm{norm}}
= \frac{1}{n}\sum_{i=1}^{n}
\mathrm{clip}\!\left(
\frac{\mathrm{IoU}(S_g^i, S_t^i) - \mathrm{IoU}(S_o^i, S_t^i)}
{1 - \mathrm{IoU}(S_o^i, S_t^i)}, 0, 1
\right).
\end{align}
Accuracy is a headroom-normalised improvement, where $1$ means the model fully traversed the original-to-target gap. 

\subsection{Training}
\label{sec:exp_training}
Beyond evaluation, we use BenchCAD as a training resource to test whether its operation breadth and standard-anchored families yield measurable capability gains, and whether these gains transfer beyond the trained families. We train an open Qwen3-VL-2B baseline reported in the bottom block of Table~\ref{tab:codegen_unified}, comparing matched-compute SFT and RL settings that differ only in training data composition. 
% \hc{Need to polish this paragraph, clearly describing the training methods}
\textbf{SFT.} We train three variants with the same optimizer, schedule, and held-out evaluation set: \emph{iid} uses BenchCAD plus extrusion-heavy auxiliary data, \emph{ood} follows the same recipe but removes 10 mechanical families, and \emph{baseline} uses no BenchCAD data.
\textbf{RL.} Starting from each SFT checkpoint, we apply an on-policy GRPO-style objective with reward $r{=}0.2\,\mathrm{ess}{+}0.8\,\mathrm{IoU}$ and $r{=}-1$ for parse errors outputs; the OOD-RL run also excludes the held-out OOD families. We report per-operation recall ablations in Table~\ref{tab:op_recall_train}, with full training details and curves in Appendix~\ref{app:training}.

