\section{Introduction}
\label{sec:intro}

Programmatic computer-aided design --- writing parametric scripts in CadQuery, OpenSCAD, or Fusion's Python API that compile to manufacturable solid geometry --- has become the natural interface between large language models and the physical-design pipeline. A vision-language model (VLM) that reads an engineering sketch, emits executable CAD code, answers dimensional queries about that code, and revises its own output to natural-language instructions would compress weeks of mechanical drafting into seconds, and several recent works have begun to deliver pieces of this promise~\citep{Khan2024,Guan2025,Rukhovich2025,Alrashedy2025,Kolodiazhnyi2026}. Yet a careful reader of these benchmarks notices an awkward pattern: the models that score highest on Chamfer distance often produce parts that \emph{look} correct in renders but fail every parametric query against the ground truth. Asked to reconstruct a flanged bushing from four canonical views, a state-of-the-art reasoning model emits a CadQuery script whose flange diameter, bore ratio, and chamfer placement are all wrong by 5--20\%, and yet the rendered solid is visually convincing enough to pass a single end-to-end metric. \textbf{The geometry passes the eye; it fails the calliper.}

This pattern is invisible to existing CAD code-generation benchmarks because they collapse three distinct capabilities into a single score. We argue that the image-to-code pipeline is best understood as a three-rung \emph{parametric pyramid}: at the base, \textbf{visual perception and 3D reconstruction}, where the model integrates four orthographic views into a coherent volumetric understanding; in the middle, \textbf{geometric-to-parametric abstraction}, where it identifies the parametric structure underlying that volume (which dimensions are bores, which are wall thicknesses, which are ratios fixed by industrial standards); and at the top, \textbf{parametric-to-code synthesis}, where it translates the parametric description into syntactically valid, executable CadQuery code. A single Chamfer-distance score collapses all three; it tells us a model failed but not \emph{which rung gave way}. Prior CAD code-generation benchmarks reside near the base of this pyramid --- Text2CAD~\citep{Khan2024} supplies natural-language conditioning for sketch+extrude command sequences over DeepCAD~\citep{Wu2021}; CAD-Coder~\citep{Guan2025} applies SFT and GRPO with a Chamfer reward to produce CadQuery code from text; the CAD-Recode/cadrille/CADEvolve lineage~\citep{Rukhovich2025,Kolodiazhnyi2026,Elistratov2026} reverse-engineers point clouds and multi-view images into CadQuery via large procedural training corpora --- but none of them probe the middle rung directly, and none isolate the rungs from one another.

Three structural limitations compound this measurement gap. \textbf{While} every existing CAD code-generation corpus is dominated by sketch-and-extrude operations --- DeepCAD, Text2CAD, CAD-Coder, and CAD-Recode collectively cover only two distinct CadQuery primitives and offer no revolution, lofting, sweeping, twist-extrusion, helical sketches, or shells, the operations that distinguish a real industrial part from a stack of boxes --- real engineering practice routinely composes 20+ such operations within a single component. \textbf{Conversely,} the benchmark with the broadest manual coverage, CADPrompt~\citep{Alrashedy2025}, contains only 200 expert-authored examples without family taxonomy, difficulty stratification, or scale-invariant prompts; its absolute-millimetre cues leak the answer to every ratio-based query that a properly designed numeric QA task would ask. \textbf{Furthermore,} ground truth across all four prior works is either parsed without re-execution (DeepCAD), filtered only by Chamfer threshold (CAD-Coder, CAD-Recode), or limited to a few hundred samples (CADPrompt) --- and none use a rotation-invariant IoU, so a geometrically correct but axis-permuted solid is silently penalised. Critically, no prior CAD benchmark provides an \emph{instruction-guided code-editing task} with verified before/after pairs, despite editing being the dominant use case in industrial CAD practice.

To address these gaps, we introduce \textbf{BenchCAD}, a CAD code-generation benchmark designed around three principles: industrial-standard anchoring, operation breadth, and capability decomposition. The dataset comprises 20{,}143 procedurally generated parts spanning 106 parametric families, with 55\% of families bound to ISO, DIN, EN, ASME, or IEC specification tables --- DIN 338 twist drills, ISO 23509 bevel gears, DIN 2095 compression springs, DIN 8187 roller chains, and so on, sampled at parameter values drawn from real specification ranges, not arbitrary geometry. The CadQuery operations exercised span 45+ distinct API calls including twist-extrusion, lofting, sweeping, helical sketches, and rectangular and polar patterns --- between 9$\times$ and 22$\times$ broader than prior corpora. Every record is execution-validated: the CadQuery source is re-run inside a sandbox, the resulting STEP is voxelised at 64$^3$ resolution, and a 6-orientation rotation-invariant 3D IoU against a reference solid must reach 0.99 for the record to enter the verified split. Atop this dataset we define \textbf{five evaluation tasks} --- \texttt{img2cq}, \texttt{qa\_img}, \texttt{qa\_code}, \texttt{edit\_img}, and \texttt{edit\_code} --- designed so that score \emph{differences} across tasks isolate which rung of the parametric pyramid is the bottleneck.

Across our evaluation of 30+ frontier models, the diagnostic differential is striking. Even the strongest reasoning models --- GPT-5, Claude 4.6 Opus, o3 --- score 15--20 percentage points lower on image-conditioned numeric QA than on the matched code-conditioned variant; this gap survives chain-of-thought prompting, persists across the 1B-to-78B Qwen2.5-VL and InternVL3 scaling series, and is unchanged by supplying eight views instead of four. We name this systematic image-versus-code gap the \textbf{Vision Bottleneck}: the dominant remaining capability deficit in programmatic CAD is not at the code-synthesis rung but at the visual-perception rung. On the editing task, we additionally observe that 64\% of nominally successful edits exhibit \textbf{Edit Leakage} --- the requested change is applied but unrelated parametric features are corrupted --- and that multi-step edits requiring parameter-dependency reasoning collapse to under 15\% pass rate across every evaluated model. Together these findings suggest that the path forward lies in training procedures explicitly aware of the parametric-symbolic structure of CAD geometry, rather than continued scaling of code-finetuned VLMs.

\paragraph{Our contributions are threefold.}
\begin{enumerate}[leftmargin=1.4em,topsep=4pt,itemsep=4pt]
  \item \textbf{The BenchCAD dataset and CadGen pipeline.} We release 20{,}143 verified parametric CAD parts spanning 106 families (55\% anchored to ISO/DIN/EN/ASME/IEC specification tables), exercising 45+ distinct CadQuery operations, and supplemented by a 433-pair instruction-guided edit subset, a 530-sample stratified Lite split for rapid leaderboards, and a 162{,}000-pair training corpus derived from GenCAD~\citep{GenCAD2025}. Underlying the dataset is CadGen, a procedural construction pipeline integrating standard-table sampling, op-list emission, sandboxed execution under a 64$^3$ rotation-invariant 3D IoU $\geq 0.99$ verification, and Croissant 1.0 metadata; all releases are publicly hosted under \texttt{BenchCAD/cad\_bench} on Hugging Face under CC-BY-4.0.
  \item \textbf{The first capability-decomposed CAD code-generation benchmark, including a verified parametric edit task.} We define five evaluation tasks --- \texttt{img2cq}, \texttt{qa\_img}, \texttt{qa\_code}, \texttt{edit\_img}, \texttt{edit\_code} --- designed so that the score contrast between paired tasks directly isolates which rung of the parametric pyramid is the bottleneck for a given model. To our knowledge, BenchCAD-Edit is the first public CAD benchmark with execution-verified before/after pairs and a non-target preservation metric, distinguishing target-feature \emph{success} from program-wide \emph{locality}.
  \item \textbf{The Vision Bottleneck and Edit Leakage diagnostics.} We evaluate 30+ frontier vision-language and code-language models --- including reasoning, non-reasoning, and CAD-specialised systems --- and identify two systematic phenomena: a 15--20 point gap between code-conditioned and image-conditioned numeric QA scores (the \emph{Vision Bottleneck}) that survives chain-of-thought prompting, parameter scaling from 1B to 78B in two open-source families, and view-count augmentation; and an Edit Leakage rate of 64\% for the strongest reasoning models, where target edits succeed but unrelated parametric features are silently corrupted. These findings refocus the CAD-LM research agenda from code-synthesis improvements onto visual-to-parametric reconstruction and parameter-dependency reasoning.
\end{enumerate}
