\section{Transfer Baselines and an Open BenchCAD-Trained Reference}
\label{sec:transfer}

\subsection{Transfer of the CAD-Recode/cadrille/CADEvolve Lineage}
The CAD-Recode/cadrille/CADEvolve lineage~\citep{Rukhovich2025,Kolodiazhnyi2026,Elistratov2026} represents the current state of the art on existing CAD code-generation benchmarks (DeepCAD image IoU 92.6 for CADEvolve; Fusion360 image IoU 87.2). All three release inference-only checkpoints sharing the Qwen2-VL-2B backbone with multi-view image input compatible with BenchCAD's render protocol. We evaluate the two latest publicly released checkpoints --- \texttt{maksimko123/cadrille-rl} and \texttt{kulibinai/cadevolve-rl1} --- on BenchCAD's \texttt{img2cq} task using the same scoring pipeline applied to all other models.

\paragraph{Headline transfer drop.} Despite scoring $>$90\% IoU on their respective evaluations, both models suffer substantial degradation on BenchCAD. Table~\ref{tab:transfer} reports gaps of 32 and 28 points on the headline IoU metric, with the steepest drops concentrated in the standard-anchored hard-tier families (helical gears, twist drills, coil springs) and in operations not exercised during their training (twist-extrusion, lofting, sweeping, helical sketches). The Vision Bottleneck pattern (\S\ref{sec:exp_capability}) is also reproduced: cadrille-RL's image-conditioned numeric QA score is 17 points lower than its code-conditioned counterpart, matching the systematic gap observed for non-CAD-specialised frontier models.

\paragraph{Why the gap is honest, not artefactual.} We replicate the lineage's render protocol (8-view 238$\times$238 grid; cube normalisation to $[-100, 100]^3$) for the transfer evaluation, eliminating mismatches in viewing geometry as a confound. We further verify that the released models reach the published IoU values on a held-out 200-sample DeepCAD slice within $\pm$0.5 points, establishing that our scoring infrastructure does not systematically penalise their outputs. The remaining gap on BenchCAD is therefore a true generalisation deficit: training corpora restricted to sketch+extrude do not transfer to families requiring helical sweeps, parametric gear teeth, or DIN-anchored standard parts.

\input{tables/tab_transfer}

\subsection{An Open BenchCAD-Trained Baseline}
To bound the difficulty of BenchCAD with publicly reproducible numbers, we release a baseline model trained directly on the dataset. We fine-tune Qwen2-VL-2B~\citep{Qwen2VL} on a mixture of the 162K-pair BenchCAD-GenCAD corpus and the 20{,}143-record BenchCAD-Synth split (image$\to$code), training for 2 epochs at learning rate $1\!\times\!10^{-5}$ on 8$\times$A800-80GB GPUs ($\approx$9 GPU-hours total). We do not apply reinforcement learning; this baseline targets reproducibility, not state of the art. Training script, data manifest, and resulting checkpoint are released under MIT licence. As Table~\ref{tab:transfer} shows, this baseline reaches an aggregate score of 18.4\% on BenchCAD-Lite --- comparable to mid-tier proprietary models and substantially below the same-architecture cadrille-RL release.

This baseline is intentionally weak. Its purpose is to provide a community lower bound and to make the transfer-baseline gaps interpretable: any improvement attributable to procedural data scaling (cadrille's 1M; CADEvolve's 2.7M), to multi-task pre-training (cadrille's pc/img/text mixing), or to RL fine-tuning (Dr.CPPO with IoU reward) appears as a contrast against this open baseline rather than against an opaque private model.

\paragraph{Implication for the field.} The transfer experiment validates the position adopted in \S\ref{sec:related}: existing CAD code-generation benchmarks are saturating against a narrow operation distribution and a narrow part vocabulary, and SOTA model improvements are increasingly within-distribution rather than out-of-distribution. BenchCAD reopens out-of-distribution evaluation by exposing the operation-coverage and standard-anchoring gaps that prior protocols cannot measure.
